### 2018-05-28 msc_diploma_cubesat_galgoczi.tex
aa

G\'abor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations. Useful comments on detectors made Dezs\"o Varga's advices on detectors were highly appreciated. The model of the satellite was provided by Tarcai Norbert and Wágner Olivér from C3S LLC. Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.

>>>>

G\'abor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations. Useful comments on detectors made Dezs\"o Varga's advices on detectors were highly appreciated. The model of the satellite was provided by Norbert Tarcai and Olivér Wágner from C3S LLC. The experimental data that was needed for the simulation was provided by Kento Torigoe and his colleges from the University of Hiroshima. The energy spectrum of cosmic electrons was deduced by Jakub Ripa. Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.
